Seperate assembly VAR Transcripts (Corset) DE Analysis

### 2017-11-08 domain_level/TextS4_domain_tree_analysis.Rmd
added in hmmer uproc analysis in response to reviewer comments

gg <- ggplot(sigUp_norm_counts_clus_df, aes(x=Phenotype, y=RPKM
                                       , colour=Phenotype))
gg <- gg + geom_boxplot(outlier.shape = NA) + geom_jitter(width = 0.2, height = 0)
gg <- gg + facet_wrap(~`Domain Cluster`) + theme_bw()
gg <- gg + scale_colour_manual(values = colors) + scale_y_log10()
gg
```

>>>>

combined_rask_new_df <- rbind(sigUp_norm_counts_clus_df, sigUp_norm_counts_df)

gg <- ggplot(combined_rask_new_df, aes(x=Phenotype, y=RPKM
                                       , colour=Phenotype))
gg <- gg + geom_boxplot(outlier.shape = NA) + geom_jitter(width = 0.05, height = 0)
gg <- gg + facet_wrap(~`Domain Cluster`, nrow=1)
gg <- gg + scale_colour_manual(values = colors) + scale_y_log10()
gg <- gg + theme_bw()
gg <- gg +  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())
gg <- gg + theme(panel.spacing.x=unit(0, "lines"),panel.spacing.y=unit(1, "lines"))
gg <- gg + theme(strip.text.x = element_text(angle = 90))
gg
```

### 2017-11-08 transcript_level/TextS2_combined_assembly_transcript_analysis.Rmd
added in hmmer uproc analysis in response to reviewer comments

>>>>

A similar plot but in a different format
```{r}
combined_length_df <- fread("./data/combined_assembly_transcript_lengths.csv"
                            , data.table = FALSE)
combined_length_matrix <- matrix(combined_length_df[,2], ncol=1,
                               dimnames = list(row=combined_length_df[,1],
                                               col="len"))
rpkm_combined <- counts(dds, normalized=FALSE)
combined_length_vector <- combined_length_matrix[rownames(rpkm_combined),]
combined_lib_size <- colSums(rpkm_combined)
rpkm_combined <- (t(t(rpkm_combined)/combined_lib_size)/combined_length_vector)*10^9
rpkm_combined <-  rpkm_combined[rownames(rpkm_combined) %in% rownames(resUp),]
rpkm_combined <- rpkm_combined + 1
# combined_rask_new_df <- counts(dds, normalized=TRUE)
# sigUp_norm_counts <- tran_counts[rownames(tran_counts) %in% rownames(resUp),]
# 
# percent_counts <- t(t(sigUp_norm_counts)/colSums(tran_counts))

sigUp_norm_counts_df <- melt(rpkm_combined)
colnames(sigUp_norm_counts_df) <- c("Transcript", "Isolate", "RPKM")
sigUp_norm_counts_df$disease[grepl("^S.*",sigUp_norm_counts_df$Isolate)]<-"severe"
sigUp_norm_counts_df$disease[!grepl("^S.*",sigUp_norm_counts_df$Isolate)]<-"non-severe"
colnames(sigUp_norm_counts_df) <- c("Transcript", "Isolate", "RPKM", "Phenotype")

gg <- ggplot(sigUp_norm_counts_df, aes(x=Phenotype, y=RPKM
                                       , colour=Phenotype))
gg <- gg + geom_boxplot(outlier.shape = NA) + geom_jitter(width = 0.05, height = 0)
gg <- gg + facet_wrap(~Transcript, nrow=1)
gg <- gg + scale_colour_manual(values = colors) + scale_y_log10()
gg <- gg + theme_bw()
gg <- gg +  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())
gg <- gg + theme(panel.spacing.x=unit(0, "lines"),panel.spacing.y=unit(1, "lines"))
gg <- gg + theme(strip.text.x = element_text(angle = 90))
gg
```

### 2017-11-08 transcript_level/TextS3_seperate_assembly_CORSET_analysis.Rmd
added in hmmer uproc analysis in response to reviewer comments

>>>>

A similar plot but in a different format
```{r}
clustered_length_df <- fread("./data/sig_clusters_combined_length.csv"
                            , data.table = FALSE)
clustered_length_matrix <- matrix(clustered_length_df[,2], ncol=1,
                               dimnames = list(row=clustered_length_df[,1],
                                               col="len"))
rpkm_clustered <- counts(dds, normalized=FALSE)
clustered_lib_size <- colSums(rpkm_clustered)

rpkm_clustered <- rpkm_clustered[rownames(rpkm_clustered) %in% rownames(SigUp),]

clustered_length_vector <- clustered_length_matrix[rownames(rpkm_clustered),]

rpkm_clustered <- (t(t(rpkm_clustered)/clustered_lib_size)/clustered_length_vector)*10^9
rpkm_clustered <- rpkm_clustered + 1

# tran_counts <- counts(dds, normalized=TRUE)
# sigUp_norm_counts <- tran_counts[rownames(tran_counts) %in% rownames(SigUp),]
# 
# percent_counts <- t(t(sigUp_norm_counts)/colSums(tran_counts))

sigUp_norm_counts_df <- melt(rpkm_clustered)
colnames(sigUp_norm_counts_df) <- c("Transcript", "Isolate", "RPKM")
sigUp_norm_counts_df$disease[grepl("^S.*",sigUp_norm_counts_df$Isolate)]<-"severe"
sigUp_norm_counts_df$disease[!grepl("^S.*",sigUp_norm_counts_df$Isolate)]<-"non-severe"
colnames(sigUp_norm_counts_df) <- c("Transcript Clusters", "Isolate", "RPKM", "Phenotype")

gg <- ggplot(sigUp_norm_counts_df, aes(x=Phenotype, y=RPKM
                                       , colour=Phenotype))
gg <- gg + geom_boxplot(outlier.shape = NA) + geom_jitter(width = 0.05, height = 0)
gg <- gg + facet_wrap(~`Transcript Clusters`, nrow=1)
gg <- gg + scale_colour_manual(values = colors) + scale_y_log10()
gg <- gg + theme_bw()
gg <- gg +  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())
gg <- gg + theme(panel.spacing.x=unit(0, "lines"),panel.spacing.y=unit(1, "lines"))
gg <- gg + theme(strip.text.x = element_text(angle = 90))
gg
```
